Precise Weed and Maize classification through Convolutional Neuronal Networks

### 2017-07-21 PaperBCJ.tex
cambios21jul
cambios 1

Deep Learning has played an important role in modern times, being widely used in artificial vision applications and specifically in pattern recognition. The versatility of deep learning has positioned it as a fit tool used in many fields of application, among which is precision agriculture. This paper presents a study of a convolutional neural network with two classes, applied for the classification between maize plants and weeds in real time, focused on maize crops in their initial development stages. The algorithm has two stages, segmentation of images and classification. Segmentation is intended to separate the target plant from the original image. While the classification is possible through a convolutional neural network, previously trained with a dataset generated through the segmentation stage. The performance of the network is illustrated by analysis and comparisons with different network architectures, then with the network that presented better results in training, (revisar esta linea) we experimented by modifying its number of filters, to analyze their behavior. Finally, the resulting network was tested on different processors to compare classification times.\\

>>>>

Deep Learning has played an important role in modern times, being widely used in artificial vision applications and specifically in pattern recognition. The versatility of deep learning has positioned it as a fit tool used in many fields of application, among which is precision agriculture. This paper presents a study of a convolutional neural network with two classes applied for the classification between maize plants and weeds in real time, focused on maize crops in their initial development stages. The algorithm has two stages, segmentation of images and classification. Segmentation is intended to separate the target plant from the original image, while classification is meant to identify what images belong to the two classes by means of a convolutional neural network previously trained with a dataset generated through the segmentation stage. The performance of the network was analyzed and compared with different network architectures. The network architecture that presented the best training results was chosen, we experimented by modifying its number of filters, to analyze their behavior. Finally, the resulting network was tested on different processors to compare classification times.\\
